---
title: "authorise"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{authorise}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(datastewardr)
```

To get API access to DMPonline, you will need your API access token.

Login to <https://dmponline.dcc.ac.uk> and go to Edit profile > API Access.

Then use the function `set_env_var()` to open the *.Renviron* file and replace
the placeholders with your email and access token.

```
DMPONLINE_EMAIL=<your.dmponline.email@example.com>
DMPONLINE_TOKEN=<your.access.token>
```

These will be automatically accessed when using functions in the **datastewardr**
package. When using API endpoints for v0, your access token will be used directly
in the header of each request. For v1 requests, the token and email will be used
to generate a bearer token, which will be cached for future requests until you
leave your R session.
